Mixture-of-interests models for representing users with diverse interests

### 2017-11-03 paper/paper.tex
Add number of mixtures sensitivity table.

\documentclass[sigchi]{acmart}

\usepackage{booktabs}
\usepackage{commath}
\usepackage{threeparttable}

@@

@@

How $U_i$ and $A_i$ are obtained differs between the three evaluated models. In the Mixture-LSTM model, $U_{it}$ and $A_{it}$ (now indexed by $t$, their position in the sequence of interactions) are linear functions of the hidden state of an LSTM layer trained on the user's previous interactions, $z_{it}$:
\begin{equation}
  z_{it} = \mathrm{LSTM}\left(e_{i1}, e_{i2}, \ldots, e_{it}\right).
\end{equation}
Given $z_{it}$, the $m$-th row of $U_{it}$ and $A_{it}$ is given by
\begin{equation}
\begin{aligned}
  u^m_{it} &= W^U_mz_{it} + B^U_m\\
  a^m_{it} &= W^A_mz_{it} + B^A_m,\\
\end{aligned}
\end{equation}
where $W^U_m$, $W^A_M$, $B^U_m$, and $B^A_m$ are the learned projection matrices. These are common across all users, representing a modest increase in the total number of model parameters.

@@

\begin{table*}[htbp]
\begin{threeparttable}
\caption{Experimental results}
\label{tb:results}
\begin{tabular}{lrrr}
\toprule
 Model               &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
 LSTM                &          0.0901 &   0.1502 &          0.1158 \\
 Mixture-LSTM        &          0.0999 &   0.1889 &          0.1358 \\
 Linear Mixture-LSTM &          0.0000 &   0.1484 &          0.1163 \\
 \midrule
 Bilinear            &          0.0999 &   0.1001 &          0.0738 \\
 Projection Mixture  &          0.0983 &   0.0698 &          0.0712 \\
 Embedding Mixture   &          0.0952 &   0.1696 &          0.0853 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond: how many items can be scored per millisecond
\item[3] Ratio of binary PPMS to real-valued PPMS
\item[4] Ratio of memory required to store binary vs. real-valued parameters
}
\end{tablenotes}
\end{threeparttable}
\end{table*}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{commath}
\usepackage{threeparttable}

@@

In this paper, we propose and evaluate representing users as mixtures of several distinct tastes, represented by distinct taste vectors. Each of the taste vectors is coupled with an attention vector, describing how competent it is at evaluating any given item. The user's preference is then modelled as a weighted average of all the user's tastes, with the weights given by how relevant each taste is to evaluating a given item.

We apply this model to both traditional implicit feedback factorization models, and to more recent models using recurrent neural networks. In both cases, our mixture-of-interests models handily outperform single-representation models on standard ranking quality metrics. In the case of deep recurrent sequence models, this improvement is achieved at a very modest cost to to the model complexity, making our model a straightforward improvement over existing methods.

@@

How $U_i$ and $A_i$ are obtained differs between the three evaluated models. In the Mixture-LSTM model, $U_{it}$ and $A_{it}$ (now indexed by $t$, their position in the sequence of interactions) are linear functions of the hidden state of an LSTM layer trained on the user's previous interactions, $z_{it}$:
\begin{equation}
  z_{it} = \mathrm{LSTM}\left(e_{i1}, e_{i2}, \ldots, e_{it}\right).
\end{equation}
Given $z_{it}$, the $m$-th row of $U_{it}$ and $A_{it}$ is given by
\begin{equation}
\begin{aligned}
  u^m_{it} &= W^U_mz_{it} + B^U_m\\
  a^m_{it} &= W^A_mz_{it} + B^A_m,\\
\end{aligned}
\end{equation}
where $W^U_m$, $W^A_M$, $B^U_m$, and $B^A_m$ are the learned projection matrices. These are common across all users, representing a modest increase in the total number of model parameters. Note that the LSTM network only needs to be run once to obtain the full user representation.

@@

\begin{table}[htbp]
\begin{threeparttable}
\caption{Experimental results}
\label{tb:results}
\begin{tabular}{lrrr}
\toprule
 Model               &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
 LSTM                &          0.0901 &   0.1502 &          0.1158 \\
 Mixture-LSTM        &          0.0999 &   0.1889 &          0.1358 \\
 Linear Mixture-LSTM &          0.0000 &   0.1484 &          0.1163 \\
 \midrule
 Bilinear            &          0.0999 &   0.1001 &          0.0738 \\
 Projection Mixture  &          0.0983 &   0.0698 &          0.0712 \\
 Embedding Mixture   &          0.0952 &   0.1696 &          0.0853 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond: how many items can be scored per millisecond
\item[3] Ratio of binary PPMS to real-valued PPMS
\item[4] Ratio of memory required to store binary vs. real-valued parameters
}
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}
\caption{Effect of number of mixture components}
\label{tab:nummixtures}
\begin{subtable}{\columnwidth}
\caption{Sequence models}
\begin{tabular}{rrrr}
\toprule
   Mixture components &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
                    2 &          0.0921 &   0.1538 &          0.1262 \\
                    4 &          0.0999 &   0.1689 &          0.1304 \\
                    6 &          0.0991 &   0.1889 &          0.1358 \\
                    8 &          0.0982 &   0.1865 &          0.1327 \\
\bottomrule
\end{tabular}
\end{subtable}
\begin{subtable}{\columnwidth}
\caption{Factorization models}
\begin{tabular}{rrrr}
\toprule
   Mixture components &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
                    2 &          0.0952 &   0.1343 &          0.0797 \\
                    4 &          0.0952 &   0.1583 &          0.0840 \\
                    6 &          0.0913 &   0.1612 &          0.0811 \\
                    8 &          0.0907 &   0.1696 &          0.0853 \\
\bottomrule
\end{tabular}
\end{subtable}\end{table}
